What Can Stack Traces Tell us about of the use Exceptions in Java?

### 2014-07-11 android-stacks.tex
Cross-coding of exception types

To better understand the root causes reported on stacks, we performed a categorization 
study on which the top 100 root causes reported on stack-issues were manually inspected.
The characterization process consisted of classifiying each exception in one of the
chategories listed on Table X, based on the inspection of source code, Javadoc, 
or additional documentation related to the exception.

\begin{table}
  \centering
  \begin{tabular}{|p{2cm}| p{5cm}|}
    \hline
    \bfseries{Category} & \bfseries{Description} \\
    \hline
      Programming logic &  Exceptions implicitly  thrown by the JVM when the 
evaluation of an expression violates the normal semantics of language (e.g., 
out-of-bounds array index, division-by-zero, access to a null reference). 
Such exceptions are usually defined on java.lang and java.util packages. \\ \hline
      Resources (IO)                         & Exception releated to the manipulation of IO resources or device  (e.g., file, network) \\ \hline
      Security                               & Exception releated to security issues (e.g. password validation, criptography) \\ \hline
      Concurrency                            & Exceptions related to multi-threaded programming \\ \hline
      Backward compatibility                 &  A list of exceptions related to backward compatibility - a complete list can be found here [ref]  \\ \hline
      Reflection                             & Exceptions related to Java reflection library  \\ \hline
      Specific                & Exceptions created for specific applications, frameworks or libraries \\ \hline
      General (Exception, Error, Runtime)    & The top level exceptions in Java    \\ \hline
    \hline
  \end{tabular}
  \caption{Categories description.}
  \label{tab:categories}
\end{table}

>>>>

To better understand the root causes reported on stacks, we categorized the top
100 distinct exception types in in one of the chategories listed on
Table~\ref{tab:categories}, based on the inspection of source code, Javadoc, or
additional documentation related to the exception. To ensure the quality
of the classification, three independent coders classified a randomly selected
sample of 25 exception types (from the total 100) using the same categories;
the interater agreement was high (96\%). We can therefore assume that the
categories are descriptive enough for covering the whole range of exception
types that can occur in real world Java projects.

\begin{table}
  \centering
  \begin{tabular}{|p{2cm}| p{5cm}|}
    \hline
    \bfseries{Category} & \bfseries{Description} \\
    \hline
      Programming logic &  Exceptions implicitly  thrown by the JVM when the 
evaluation of an expression violates the normal semantics of language (e.g., 
out-of-bounds array index, division-by-zero, access to a null reference). 
Such exceptions are usually defined on java.lang and java.util packages. \\ \hline
      Resources (IO)                         & Exception releated to the manipulation of IO resources or device  (e.g., file, network) \\ \hline
      Security                               & Exception releated to security issues (e.g. password validation, criptography) \\ \hline
      Concurrency                            & Exceptions related to multi-threaded programming \\ \hline
      Backward compatibility                 &  A list of exceptions related to backward compatibility - a complete list can be found here [ref]  \\ \hline
      Reflection                             & Exceptions related to Java reflection library  \\ \hline
      Specific                & Exceptions created for specific applications, frameworks or libraries \\ \hline
      General (Exception, Error, Runtime)    & The top level exceptions in Java    \\ \hline
    \hline
  \end{tabular}
  \caption{Description of categories.}
  \label{tab:categories}
\end{table}
